---
title: "20221209 - 2.mgm"
output:
  word_document: default
  html_document: default
date: "2022-12-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)
p_load(tidyverse, here, sjlabelled, stringr, glue, EGAnet, janitor, haven, 
       ggpubr, gridExtra, dplyr, GGally, qgraph, sjmisc, igraph, sjPlot,
       grid, psych, stargazer, mgm, backbone, ggplot2, tnet, ggrepel,
       NetworkComparisonTest, Matrix, bootnet, matrixcalc, openxlsx, devtools, jtools)


```


# Input

```{r}
W3 = readRDS((here("Input", "W3.rds")))
```

# Processing

## Network objects

```{r}
## network objects
type <-c("g","g","c","g","c","g","g","g","g","g","g","g","c","c","c","g","c",
         "c","g","c","g","g","g")

level <-c("1","1","2","1","2","1","1","1","1","1","1","1","2","2","2","1","2"
          ,"2","1","2","1","1","1")

shortnames <- c(
"vac_bad",
"vac_free",
"low_worry",
"low_risk",
"conspiracy",
"nat",
"int_locus",
"low_col_resp",
"PTV_L",
"PTV_5SM",
"PTV_BOI",
"distrust_sci",
"pray",
"media",
"female",
"young",
"low_educ",
"rural",
"eco_insec",
"hesitancy",
"low_comp",
"distrust_gov",
"distrust_inst")

longnames <- c(
"Vaccine bad for health",
"Against mandatory vaccination",
"Low worry about infection",
"Low risk perception",
"Endorsing conspiracy theories",
"Trust in alternative medicine",
"Internal health locus of control",
"Low sense of collective responsability",
"Propensity to vote for L",
"Propensity to vote for 5SM",
"Propensity to vote for BOI",
"Distrust of science",
"Religion, pray",
"Digital media diet",
"Sex, female",
"Age, young",
"Educational level, low",
"Living in a rural region",
"Economic insecurity",
"Vaccine hesitancy",
"Low compliance with preventive behaviors",
"Disapproval of Government",
"Distrust of institutions")

shapes <- c(
"circle", 
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"square",
"circle",
"circle",
"circle")

# Community detection function (modified to allow for iterations)
communityStability <- function(data, type, level, iterations)
{
  
  communityMemberships <- list()
  
  for (i in 1:iterations)
  {
    fitGraph <- mgm(data, type, level, k = 2, verbatim = TRUE)
    iGraph<- graph_from_adjacency_matrix(abs
                                         (fitGraph$pairwise$wadj), "undirected", weighted =
                                           TRUE)
    communityMemberships[[i]] <- cluster_walktrap(iGraph)$membership
  }
  
  communityOverlap <- matrix(NA, length(data), length(data))
  
  for(j in 1:length(data))
  {
    
    overlapPerNode <- matrix(NA, iterations, ncol(communityOverlap))
    
    for(k in 1: iterations)
    {
      overlapPerNode[k,] <- as.numeric(communityMemberships[[k]][j] == communityMemberships[[k]])
    }
    
    communityOverlap[j,] <- apply(overlapPerNode, 2, mean)
  }
  
  diag(communityOverlap) <- 0
  
  return(list(communityMemberships = communityMemberships, communityOverlap = communityOverlap))
  
}
```
## Fit model
```{r}
set.seed(1)
FitW3 <- mgm(W3, type, level, k = 2, binarySign = TRUE)
```

## Community stability (Supplement S1)

```{r}
#LOAD THE OBJECT down below TO SAVE TIME:
CommunityStabTotal<-communityStability(W3, type, level, it=1000)

#load the object instead:
CommunityStabTotal = readRDS(here("Input", "CommunityStabTotal.rds"))
```

```{r}
# Visualize community stability 
pdf(file = '../Output/Supplement/community_stability.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(CommunityStabTotal$communityOverlap, layout = "spring", 
       theme = "Borkulo", labels = shortnames,
       nodeNames = longnames,vsize=4.0,
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
dev.off()

# Vizualise detected communities 
inputCommDetection_total<-CommunityStabTotal$communityOverlap
inputCommDetection_total[which(inputCommDetection_total <= .90)] <- 0

pdf(file = '../Output/Supplement/detected_communities.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(inputCommDetection_total, layout = "spring", theme = "Borkulo",
       labels = shortnames, nodeNames = longnames, vsize=4.0,
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
dev.off()
```

```{r}
Totalgroup_comm <- list(
 " "=c(1,2,12,20),
 " "=c(3,4),
 " "=c(5,8),
 " "=c(6,7,21),
 " "=c(9,11),
 " "=c(10,22,23),
 " "=c(13:19))

# define nice colors
Totalgroup_cols <- c("#BDE6F1","#E96479","#3FA796","#B4CFB0",
                              "#DF7861","#C3ACD0","#FFD56F")
```

## Plot no minimum (Supplement S1)

```{r}
#enables theme colorblind because we don't need to specify edge.color
inputGraphMGM <- FitW3$pairwise$wadj
signsGraphMGM <- FitW3$pairwise$signs
signsGraphMGM[which(is.na(signsGraphMGM))] <- 1
inputGraphMGM <- inputGraphMGM*signsGraphMGM

# Plot 
set.seed(1)
pdf(file = '../Output/Supplement/MGM_nomin.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames, nodeNames = longnames,
  cut = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.4, borders = FALSE)
dev.off()
```

### Plot with predictability (Article)
```{r}
#Predicted values
p_obj <- predict(FitW3, W3, errorCat = c("CC","nCC","CCmarg"), errorCon = c("R2"))

#insert them in a list, and compute different metrics for cathegorical variables
error_list <- list() 
error_list[[1]] = p_obj$errors[1,2]
error_list[[2]] = p_obj$errors[2,2]
  beyondmarg <- p_obj$errors[3,3]-p_obj$errors[3,5]
  error_list[[3]] = c(p_obj$errors[3,5],beyondmarg)
error_list[[4]] = p_obj$errors[4,2]
  beyondmarg <- p_obj$errors[5,3]-p_obj$errors[5,5]
  error_list[[5]] = c(p_obj$errors[5,5],beyondmarg)
error_list[[6]] = p_obj$errors[6,2]
error_list[[7]] = p_obj$errors[7,2]
error_list[[8]] = p_obj$errors[8,2]
error_list[[9]] = p_obj$errors[9,2]
error_list[[10]] = p_obj$errors[10,2]
error_list[[11]] = p_obj$errors[11,2]
error_list[[12]] = p_obj$errors[12,2]
error_list[[13]] = p_obj$errors[13,2]
  beyondmarg <- p_obj$errors[14,3]-p_obj$errors[14,5]
  error_list[[14]] = c(p_obj$errors[14,5],beyondmarg)
  beyondmarg <- p_obj$errors[15,3]-p_obj$errors[15,5]
  error_list[[15]] = c(p_obj$errors[15,5],beyondmarg)
error_list[[16]] = p_obj$errors[16,2]
  beyondmarg <- p_obj$errors[17,3]-p_obj$errors[17,5]
  error_list[[17]] = c(p_obj$errors[17,5],beyondmarg)
error_list[[18]] = p_obj$errors[18,2]
error_list[[19]] = p_obj$errors[19,2]
  beyondmarg <- p_obj$errors[20,3]-p_obj$errors[20,5]
  error_list[[20]] = c(p_obj$errors[20,5],beyondmarg)
error_list[[21]] = p_obj$errors[21,2]
error_list[[22]] = p_obj$errors[22,2]
error_list[[23]] = p_obj$errors[23,2]

# List for Colors 
color_list <- list()
color_list[[1]] = "#90B4D4"
color_list[[2]] = "#90B4D4"
color_list[[3]] = c("#ffa500", "#ff4300")
color_list[[4]] = "#90B4D4"
color_list[[5]] = c("#ffa500", "#ff4300")
color_list[[6]] = "#90B4D4"
color_list[[7]] = "#90B4D4"
color_list[[8]] = "#90B4D4"
color_list[[9]] = "#90B4D4"
color_list[[10]] = "#90B4D4"
color_list[[11]] = "#90B4D4"
color_list[[12]] = "#90B4D4"
color_list[[13]] = "#90B4D4"
color_list[[14]] = c("#ffa500", "#ff4300")
color_list[[15]] = c("#ffa500", "#ff4300")
color_list[[16]] = "#90B4D4"
color_list[[17]] = c("#ffa500", "#ff4300")
color_list[[18]] = "#90B4D4"
color_list[[19]] = "#90B4D4"
color_list[[20]] = c("#ffa500", "#ff4300")
color_list[[21]] = "#90B4D4"
color_list[[22]] = "#90B4D4"
color_list[[23]] = "#90B4D4"
```

```{r}
# The final plot
set.seed(100)
GraphMGM<-qgraph(inputGraphMGM, pie = error_list, pieColor = color_list,
  layout = "spring", theme = "Borkulo", 
  labels = shortnames, nodeNames = longnames,
  cut = 0.10, minimum = 0.07, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.35, borders = TRUE, 
  filetype="jpg", filename=here("Output", "Article", "MGM_min_07_predictability"))
```

## Centrality estimates

```{r}
#graph with complete labels for centrality plot
GraphMGMCENT<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind",
  labels = longnames, minimum = 0,
  cut = 0.10, maximum = 1, details = TRUE,
  legend = FALSE)

#centrality Total
centMGM <- centralityTable(GraphMGMCENT,standardized = FALSE, signed = FALSE)

#CentralityPlot Total
centrality_table = centralityPlot(GraphMGMCENT, include = c("Strength"), scale = "raw",
               orderBy = "Strength", signed = FALSE) + theme_nice() + theme(axis.text.y=element_text(hjust=1))

ggsave(here("Output", "Article", "Centrality_Table.jpg"), centrality_table)
```
### Degree centrality
```{r}
#Convert to igraph
igraph_graph <- graph.adjacency(FitW3$pairwise$wadj, mode="undirected", weighted = TRUE)

#Degree centrality
degree_cent = degree(igraph_graph) 

#Merge vectors
degree_data <- data.frame(names(W3), degree_cent)
```


## ASPL

```{r}
#Shortest Path Lenght with tnet from opshal
spl_o = distance_w(FitW3$pairwise$wadj, directed=NULL, subsample=1)
spl_o <- spl_o[upper.tri(spl_o)]
aspl_o <- mean(spl_o)
```
ASPL = 1.643193

## Bootstrap (Supplement S1)

#### Edge accuracy

```{r}
#edge weight accuracy: non parametric bootstrap with 8 cores
#edgeacc =  bootnet(W3, nBoots = 1000, nCores = 8, 'mgm')

#load the object instead:
edgeacc = readRDS(here("Input", "edgeacc.rds"))

#plot 1
pdf('../Output/Supplement/robustness/edge_accuracy.pdf', height = 70, width = 50)
plot(edgeacc, labels = longnames, order = "sample")
dev.off()

#Plot 2
pdf('../Output/Supplement/robustness/edge_accuracy_CI.pdf', height = 70, width = 50)
plot(edgeacc, plot = "interval", split0 = TRUE, order="sample", labels=longnames)
dev.off()

#summary
saummary_edgeacc = summary(edgeacc, statistics = c("edge", "strength"), 
                            perNode = FALSE, rank = FALSE) 
```

#### Centrality stability (Supplement S1)

```{r}
# case dropping bootstrap
#centstab = bootnet(W3, nBoots = 1000, 'mgm', type = "case", nCores = 8)

#load the object instead:
centstab = readRDS(here("Input", "centstab.rds"))

#plot 1
pdf('../Output/Supplement/robustness/Centrality_stability.pdf', height = 70, width = 50)
plot(centstab, "Strength", perNode = TRUE, labels = longnames,
     subsetRange = c(100,50))
dev.off()

#Plot 2
pdf('../Output/Supplement/robustness/Centrality_stability_CI.pdf', height = 70, width = 50)
plot(centstab, "Strength", CIstyle =  "quantiles")
dev.off()

#CS-coefficient (result should be above 0.25, better if above 0.5)
corstab = corStability(centstab)
```

#### Testing Edge and centrality differences (Supplement S1)

```{r}
# Test: difference of weight ties 2-3 vs 4-5
differenceTest(edgeacc, 2--3, 3--4, "strength")

# Plot test results for every edge weight in the network
pdf('../Output/Supplement/robustness/test_edges.pdf', height = 70, width = 50)
plot(edgeacc, "edge", plot = "difference", onlyNonZero = TRUE, order = "sample", 
     labels = T)
dev.off()
```

```{r}
# Test: difference of strength of node 5 [conspiracy] vs 20 [hesitancy] (if the bootstrapped CI include 0, they do not differ)
test_conspiracy_vs_hesitancy = differenceTest(edgeacc, 5, 20, "strength")

# Plot test results for every edge weight in the network
pdf('../Output/Supplement/robustness/test_strenghts.pdf', height = 70, width = 50)
plot(edgeacc, "strength", order = "mean", labels = T)
dev.off()
```
## Additional robustness check (Supplement S1)
```{r}
#Creating serial number for each row
W3_robustness = W3
W3_robustness$id = 1:nrow(W3)

#Splitting randomly the original data frame in two partitions
W3_robustness_a = W3_robustness %>% dplyr::sample_frac(.50) 
W3_robustness_b = dplyr::anti_join(W3_robustness, W3_robustness_a, by = 'id') 

#Remove id variable
W3_robustness_a = W3_robustness_a %>% dplyr::select(-id)
W3_robustness_b = W3_robustness_b %>% dplyr::select(-id)

#Fitting two mgm
set.seed(1)
FitW3_robustness_a <- mgm(W3_robustness_a, type, level, k = 2, binarySign = TRUE)

set.seed(1)
FitW3_robustness_b <- mgm(W3_robustness_b, type, level, k = 2, binarySign = TRUE)
```

```{r}
#Network Comparison Test between the two mgm 
#(NO CORRECTION FOR MULTIPLE TESTING)
set.seed(1)
robustness_a_b = NCT(W3_robustness_a, W3_robustness_b, it = 1000,
      test.edges=TRUE, edges="all", 
      progressbar=TRUE, p.adjust.methods= c("none"), 
      test.centrality=TRUE, 
      centrality=c("strength"),nodes="all")

#Network Comparison Test with BONFERRONI CORRECTION:
#NO DIFFERENCES EMERGE
set.seed(1)
robustness_a_b_bonferroni = NCT(W3_robustness_a, W3_robustness_b, it = 1000,
      test.edges=TRUE, edges="all", 
      progressbar=TRUE, p.adjust.methods= c("bonferroni"), 
      test.centrality=TRUE, 
      centrality=c("strength"),nodes="all")
```


```{r}
#Visualize results of edge tests
inputNCTgraph <- FitW3_robustness_a$pairwise$wadj - FitW3_robustness_b$pairwise$wadj
inputNCTgraph[upper.tri(inputNCTgraph)][which(robustness_a_b$einv.pvals$`p-value` >= .05)] <- 0
inputNCTgraph <- forceSymmetric(inputNCTgraph)

pdf(here("Output", "Supplement", "nct.pdf"))
nct_plot = qgraph(inputNCTgraph, labels = shortnames, edge.labels = TRUE)
dev.off()
```

```{r}
#Visualize results of centrality tests
#Calculate strength
Graph_robustness_a <-qgraph(FitW3_robustness_a$pairwise$wadj, labels = shortnames) 
cent_robustness_a <- centralityTable(Graph_robustness_a)

Graph_robustness_b <-qgraph(FitW3_robustness_b$pairwise$wadj, labels = shortnames) 
cent_robustness_b <- centralityTable(Graph_robustness_b)

#isolate what is statistically different
robustness_a_b$diffcen.pval #only: media, age, reg
robustness_a_b$diffcen.real

```


## Backbone (Article)

```{r}
#model selection
backbone.suggest(FitW3$pairwise$wadj)

# application of the disparity filter
backbone_matrix <- disparity(
  inputGraphMGM,
  alpha = 0.05,
  signed = FALSE,
  mtc = "none",
  class = "original",
  narrative = TRUE)

#plot
set.seed(100)
GraphMGM<-qgraph(backbone_matrix, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames,nodeNames = longnames,
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.35, borders = FALSE, 
  filetype="jpg", filename=here("Output", "Article", "backbone.jpg"))

```


## Regressions (Supplement S1)
```{r}
#Fitting logistic regressions
model_vac_bad <- glm( hesitancy ~ vac_bad + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_vac_ob <- glm( hesitancy ~ vac_ob + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_worry <- glm( hesitancy ~ worry + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_risk <- glm( hesitancy ~ risk + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_conspiracy <- glm( hesitancy ~ conspiracy + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_nat <- glm( hesitancy ~ nat + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_h_locus <- glm( hesitancy ~ h_locus + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_he_eco <- glm( hesitancy ~ he_eco + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_L <- glm( hesitancy ~ PTV_L + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_5SM <- glm( hesitancy ~ PTV_5SM + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_BOI <- glm( hesitancy ~ PTV_BOI + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_tr_sci <- glm( hesitancy ~ tr_sci + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_pray <- glm( hesitancy ~ pray + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_media <- glm( hesitancy ~ media + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_low_comp <- glm( hesitancy ~ low_comp + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_distrust_gov <- glm( hesitancy ~ distrust_gov + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_distrust_inst <- glm( hesitancy ~ distrust_inst + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

#Additional model for final table
model_educ <- glm( hesitancy ~ educ + sex + age + reg + eco_insec, 
                data = W3, family = binomial)
  #coeff
  coeff_educ =  exp(extract_numeric(model_educ$coefficients[2]))
  
  #significance
  summary(model_educ)$coeff[-1,4] < 0.05
```

## Export regression table for additional material (Supplement S1)
```{r}
#model_vac_bad
tab_model(list(model_vac_bad),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("vac_bad"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_vac_bad.doc")
)

#model_vac_ob
tab_model(list(model_vac_ob),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("vac_ob"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_vac_ob.doc")
)

#model_worry
tab_model(list(model_worry),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("worry"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_worry.doc")
)

#model_risk
tab_model(list(model_risk),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("risk"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_risk.doc")
)

#model_conspiracy
tab_model(list(model_conspiracy),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("conspiracy"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_conspiracy.doc")
)

#model_nat
tab_model(list(model_nat),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("nat"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_nat.doc")
)

#model_h_locus
tab_model(list(model_h_locus),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("h_locus"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_h_locus.doc")
)


#model_he_eco
tab_model(list(model_he_eco),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("he_eco"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_he_eco.doc")
)

#model_PTV_L
tab_model(list(model_PTV_L),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("PTV_L"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_PTV_L.doc")
)

#model_PTV_5SM
tab_model(list(model_PTV_5SM),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("PTV_5SM"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_PTV_5SM.doc")
)

#model_PTV_BOI
tab_model(list(model_PTV_BOI),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("PTV_BOI"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_PTV_BOI.doc")
)

#model_tr_sci
tab_model(list(model_tr_sci),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("tr_sci"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_tr_sci.doc")
)

#model_pray
tab_model(list(model_pray),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("pray"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_pray.doc")
)

#model_media
tab_model(list(model_media),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("media"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_media.doc")
)

#model_low_comp
tab_model(list(model_low_comp),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("low_comp"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_low_comp.doc")
)

#model_distrust_gov
tab_model(list(model_distrust_gov),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("distrust_gov"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_distrust_gov.doc")
)

#model_distrust_inst
tab_model(list(model_distrust_inst),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("distrust_inst"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_distrust_inst.doc")
)

#model_vac_bad
tab_model(list(model_vac_bad),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("vac_bad"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_vac_bad.doc")
)

#Additional model for final table
tab_model(list(model_educ),
          show.p = TRUE,
          p.style = "stars",
          p.threshold = c(0.1, 0.05, 0.01),
          dv.labels = c("educ"),
          collapse.ci = TRUE,
          show.aic = TRUE,
          title = "Logit regression model on vaccine hesitancy",
          string.pred = " ",
          auto.label = FALSE, 
          file = here("Output", "Supplement", "regressions", "model_educ.doc")
)
```


## Scatterplot data
```{r}
#Gathering coefficients
coeff = extract_numeric(model_vac_bad$coefficients[2])
coeff[2] = extract_numeric(model_vac_ob$coefficients[2])
coeff[3] = extract_numeric(model_worry$coefficients[2])
coeff[4] = extract_numeric(model_risk$coefficients[2])
coeff[5] = extract_numeric(model_conspiracy$coefficients[2])
coeff[6] = extract_numeric(model_nat$coefficients[2])
coeff[7] = extract_numeric(model_h_locus$coefficients[2])
coeff[8] = extract_numeric(model_he_eco$coefficients[2])
coeff[9] = extract_numeric(model_PTV_L$coefficients[2])
coeff[10] = extract_numeric(model_PTV_5SM$coefficients[2])
coeff[11] = extract_numeric(model_PTV_BOI$coefficients[2])
coeff[12] = extract_numeric(model_tr_sci$coefficients[2])
coeff[13] = extract_numeric(model_pray$coefficients[2])
coeff[14] = extract_numeric(model_media$coefficients[2])
coeff[15] = extract_numeric(model_low_comp$coefficients[2])
coeff[16] = extract_numeric(model_distrust_gov$coefficients[2])
coeff[17] = extract_numeric(model_distrust_inst$coefficients[2])

  #Transform in odds ratio
  coeff_exp = unlist(lapply(coeff, exp))
```


```{r}
#Significance
summary(model_vac_bad)$coeff[-1,4] < 0.05
summary(model_vac_ob)$coeff[-1,4] < 0.05
summary(model_worry)$coeff[-1,4] < 0.05 #not significant
summary(model_risk)$coeff[-1,4] < 0.05
summary(model_conspiracy)$coeff[-1,4] < 0.05
summary(model_nat)$coeff[-1,4] < 0.05
summary(model_h_locus)$coeff[-1,4] < 0.05
summary(model_he_eco)$coeff[-1,4] < 0.05
summary(model_PTV_L)$coeff[-1,4] < 0.05
summary(model_PTV_5SM)$coeff[-1,4] < 0.05 #not significant
summary(model_PTV_BOI)$coeff[-1,4] < 0.05
summary(model_tr_sci)$coeff[-1,4] < 0.05
summary(model_pray)$coeff[-1,4] < 0.05 #not significant
summary(model_media)$coeff[-1,4] < 0.05 #not significant
summary(model_low_comp)$coeff[-1,4] < 0.05
summary(model_distrust_gov)$coeff[-1,4] < 0.05
summary(model_distrust_inst)$coeff[-1,4] < 0.05

  #vector for significance
  Significance = rep(c("Significant"),17)
  Significance[3] = "Not significant"
  Significance[10] = "Not significant"
  Significance[13] = "Not significant"
  Significance[14] = "Not significant"
```


```{r}
#Gatering strength scores
strength = centMGM %>%
  filter(measure=="Strength") %>% 
  dplyr::select(value) %>%
  filter(!row_number() %in% c(15:20))

cent_all = centMGM %>%
  filter(measure=="Strength") %>% 
  dplyr::select(value, node) %>% 
  mutate_if(is.numeric, ~round(., 2))
```


```{r}
#Gatering degree
degree_cent_graph = degree_cent[-c(15:20)]
```


```{r}
#Gathering names
names = shortnames
names = names[-c(15:20)]
```


```{r}
#Merging into a df1 (Reported in Supplement S1)
scatterplot = data.frame(names, coeff_exp, strength, Significance) %>% 
  rename(strength = value)
scatterplot$names = as.factor(scatterplot$names)
scatterplot$coeff_exp = as.numeric(scatterplot$coeff_exp)
scatterplot$strength = as.numeric(scatterplot$strength)
scatterplot$Significance = as.factor(scatterplot$Significance)

#Merging into a df2
scatterplot_degree = data.frame(names, coeff_exp, degree_cent_graph, Significance)
scatterplot_degree$degree_cent_graph = as.numeric(scatterplot_degree$degree_cent_graph)

print(scatterplot_degree)
```

## Scatterplots 
```{r}
#Strength (Article)
graph_strength = ggplot(scatterplot, aes(x=strength, y=coeff_exp, label = names)) + 
  geom_point((aes(color=Significance))) + theme_nice() + 
  geom_smooth(method=lm, se = FALSE, linetype = "dotted", color = "#DCDCDC") +
  geom_text_repel(size = 3) +
  xlab("Strength centrality") + ylab("Regression coefficient") + 
  scale_fill_discrete(labels=c('label1', 'label2'))

ggsave(here("Output", "Article", "graph_strength.jpg"), graph_strength, height = 5, width = 8)
```

```{r}
#Degree (Supplement S1)
graph_degree = ggplot(scatterplot_degree, aes(x=degree_cent_graph, y=coeff_exp, label = names)) + 
  geom_point((aes(color=Significance))) + theme_nice() + 
  geom_smooth(method=lm, se = FALSE, linetype = "dotted", color = "#DCDCDC") +
  geom_text_repel(size = 3) +
  xlab("Degree centrality") + ylab("Regression coefficient") + 
  scale_fill_discrete(labels=c('label1', 'label2'))

ggsave(here("Output", "Supplement", "graph_degree.jpg"), graph_degree, height = 5, width = 8)
```

## Final table empirical predictors (Article)
```{r}
#Df with variables that (1) are tied to hesitancy, (2) are in the backbone
final_tab = scatterplot %>% 
  mutate(degree = scatterplot_degree$degree_cent_graph) %>% 
  add_row(names = "educ", coeff_exp = 1.764246, strength = 1.061313041, 
          Significance = "Significant", degree = 10) %>% 
  filter(names %in% c("vac_free","vac_bad","low_comp","conspiracy","nat","educ")) %>% 
  mutate(edge_weight=c(0.95, 0.34, 0.34, 0.12, 0.07, 0.07)) %>% 
  relocate(Significance, .after = edge_weight) 

    #conversion of type
    final_tab$names = as.factor(final_tab$names)
    final_tab$coeff_exp = as.numeric(final_tab$coeff_exp)
    final_tab$strength = as.numeric(final_tab$strength)
    final_tab$degree = as.numeric(final_tab$degree)
    final_tab$edge_weight = as.numeric(final_tab$edge_weight)
    final_tab$Significance = as.factor(final_tab$Significance)

#Z scores
final_tab_z = final_tab %>% 
  mutate(coeff_exp = (coeff_exp - mean(coeff_exp))/sd(coeff_exp), 
         strength = (strength - mean(strength))/sd(strength),
         degree = (degree - mean(degree))/sd(degree),
         edge_weight = (edge_weight - mean(edge_weight))/sd(edge_weight)) %>% 
          mutate_if(is.numeric, ~round(., 2))
```


# Output

## Export heavy objects

```{r}
#communities
saveRDS(CommunityStabTotal, here("Input", "CommunityStabTotal.rds"))
#bootnet
saveRDS(edgeacc, here("Input","edgeacc.rds"))
saveRDS(centstab, here("Input", "centstab.rds"))
#final tab
saveRDS(final_tab, here("Input", "final_tab.rds"))
saveRDS(final_tab_z, here("Input", "final_tab_z.rds"))
```

## Edge weight to excel (Supplement S1)

```{r}
##only upper triangle without edge weigths 0 for readability
EdgeWeight_Total_half<-upper.triangle(inputGraphMGM)
EdgeWeight_Total_half[EdgeWeight_Total_half == 0] <- NA
EdgeWeightsExcel_half<- list("mgm" = EdgeWeight_Total_half)
write.xlsx(EdgeWeightsExcel_half, "../Output/Supplement/EdgeWeightsExcel_half.xlsx",
           colWidths = "auto", rowNames = TRUE)
```

