---
title: "20221209 - 2.mgm"
output: html_document
date: "2022-12-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(pacman)
p_load(tidyverse, here, sjlabelled, stringr, glue, EGAnet, janitor, haven, 
       ggpubr, gridExtra, dplyr, GGally, qgraph, sjmisc, igraph,
       grid, psych, stargazer, mgm, backbone, ggplot2, tnet,
       NetworkComparisonTest, Matrix, bootnet, matrixcalc, openxlsx, devtools, jtools)


```


# Input

```{r}
W3 = readRDS((here("Input", "W3.rds")))
```

# Processing

## Network objects

```{r}
## network objects
type <-c("g","g","c","g","c","g","g","g","g","g","g","g","g","c","c","g","c",
          "g","g","c","g","g","g")

level <-c("1","1","2","1","2","1","1","1","1","1","1","1","1","2","2","1","2",
          "1","1","2","1","1","1")

shortnames <- c(
"vac_bad",
"vac_free",
"low_worry",
"low_risk",
"conspiracy",
"nat",
"int_locus",
"low_col_resp",
"PTV_L",
"PTV_5SM",
"PTV_BOI",
"distrust_sci",
"pray",
"media",
"female",
"young",
"low_educ",
"rural",
"eco_insec",
"hesitancy",
"low_comp",
"distrust_gov",
"distrust_inst")

longnames <- c(
"Vaccine bad for health",
"Against mandatory vaccination",
"Low worry about infection",
"Low risk perception",
"Endorsing conspiracy theories",
"Trust in alternative medicine",
"Internal health locus of control",
"Low sense of collective responsability",
"Propensity to vote for L",
"Propensity to vote for 5SM",
"Propensity to vote for BOI",
"Distrust of science",
"Religion, pray",
"Digital media diet",
"Sex, female",
"Age, young",
"Educational level, low",
"Living in a rural region",
"Economic insecurity",
"Vaccine hesitancy",
"Low compliance with preventive behaviors",
"Disapproval of Government",
"Distrust of institutions")

shapes <- c(
"circle", 
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"circle",
"square",
"circle",
"circle",
"circle")

# Community detection function
communityStability <- function(data, type, level, iterations)
{
  
  communityMemberships <- list()
  
  for (i in 1:iterations)
  {
    fitGraph <- mgm(data, type, level, k = 2, verbatim = TRUE)
    iGraph<- graph_from_adjacency_matrix(abs
                                         (fitGraph$pairwise$wadj), "undirected", weighted =
                                           TRUE)
    communityMemberships[[i]] <- cluster_walktrap(iGraph)$membership
  }
  
  communityOverlap <- matrix(NA, length(data), length(data))
  
  for(j in 1:length(data))
  {
    
    overlapPerNode <- matrix(NA, iterations, ncol(communityOverlap))
    
    for(k in 1: iterations)
    {
      overlapPerNode[k,] <- as.numeric(communityMemberships[[k]][j] == communityMemberships[[k]])
    }
    
    communityOverlap[j,] <- apply(overlapPerNode, 2, mean)
  }
  
  diag(communityOverlap) <- 0
  
  return(list(communityMemberships = communityMemberships, communityOverlap = communityOverlap))
  
}
```
## Fit model
```{r}
set.seed(1)
FitW3 <- mgm(W3, type, level, k = 2, binarySign = TRUE)
```

## Community stability

```{r}
#LOAD THE OBJECT down below TO SAVE TIME:
#CommunityStabTotal<-communityStability(W3, type, level, it=1000)

#load the object instead:
CommunityStabTotal = readRDS(here("Input", "CommunityStabTotal.rds"))
```

```{r}
# Visualize community stability
pdf(file = '../Output/community_stability.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(CommunityStabTotal$communityOverlap, layout = "spring", 
       theme = "Borkulo", labels = shortnames,
       nodeNames = longnames,vsize=4.0,
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
dev.off()

# Vizualise detected communities
inputCommDetection_total<-CommunityStabTotal$communityOverlap
inputCommDetection_total[which(inputCommDetection_total <= .90)] <- 0

pdf(file = '../Output/detected_communities.pdf',paper = "USr",
    height = 9, width = 12)
qgraph(inputCommDetection_total, layout = "spring", theme = "Borkulo",
       labels = shortnames, nodeNames = longnames, vsize=4.0,
       edge.labels=FALSE, legend = TRUE, legend.cex = 0.3)
dev.off()
```

```{r}
# group variables based on TH CHECK AGAIN BASED ON THE TABLE
#Totalgroup_comm <- list(
# "Vaccine related"=c(1,2),
# "Individual/group"=c(3:8,22),
# "Context"=c(9:20,23,24),
# "Hesitancy"=c(21))

Totalgroup_comm <- list(
 " "=c(1,2,12,20),
 " "=c(3,4),
 " "=c(5,8),
 " "=c(6,7,21),
 " "=c(9,11),
 " "=c(10,22,23),
 " "=c(13:19))

# define nice colors
Totalgroup_cols <- c("#BDE6F1","#E96479","#3FA796","#B4CFB0",
                              "#DF7861","#C3ACD0","#FFD56F")
```

## Plot

```{r}
#enables theme colorblind because we don't need to specify edge.color
inputGraphMGM <- FitW3$pairwise$wadj
signsGraphMGM <- FitW3$pairwise$signs
signsGraphMGM[which(is.na(signsGraphMGM))] <- 1
inputGraphMGM <- inputGraphMGM*signsGraphMGM

# refined, no minimum 
set.seed(1)
pdf(file = '../Output/MGM_nomin.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames, nodeNames = longnames,
  cut = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.4, borders = FALSE)
dev.off()

# refined,  minimum = 0.7
set.seed(100)
pdf(file = '../Output/MGM_min_07.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.07, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.35, borders = FALSE)
dev.off()

# same but in jpg
set.seed(100)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.07, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.35, borders = FALSE, 
  filetype="jpg", filename=here("Output", "MGM_min_07.jpg"))

# refined,  minimum = 0.10
pdf(file = '../Output/MGM_min_10.pdf',paper = "USr", height = 9, width = 12)
GraphMGM<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames,nodeNames = longnames,
  cut = 0.10, minimum = 0.10, maximum = 1, 
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.3, borders = FALSE)
dev.off()
```

## Centrality estimates

```{r}
#graph with complete labels for centrality plot
GraphMGMCENT<-qgraph(inputGraphMGM, 
  layout = "spring", theme = "colorblind",
  labels = longnames, minimum = 0,
  cut = 0.10, maximum = 1, details = TRUE,
  legend = FALSE)

#centrality Total
centMGM <- centralityTable(GraphMGMCENT,standardized = FALSE, signed = FALSE)

#CentralityPlot Total
centrality_table = centralityPlot(GraphMGMCENT, include = c("Strength"), scale = "raw",
               orderBy = "Strength", signed = FALSE) + theme_nice() + theme(axis.text.y=element_text(hjust=1))

ggsave(here("Output", "Centrality_Table.jpg"), centrality_table)
```
### Degree centrality
```{r}
#Convert to igraph
igraph_graph <- graph.adjacency(FitW3$pairwise$wadj, mode="undirected", weighted = TRUE)

#Degree centrality
degree_cent = degree(igraph_graph) 

#Merge vectors
degree_data <- data.frame(names(W3), degree_cent)
```


## ASPL

```{r}
#Shortest Path Lenght
SPLMGM <- centrality(GraphMGM)$ShortestPathLengths
SPLMGM <- SPLMGM[upper.tri(SPLMGM)]
#Average shortest path length
ASPL_MGM <- mean(SPLMGM)

#Check with another function (this does not account for edge weights)
splmgm = shortest.paths(igraph_graph)
splmgm <- splmgm[upper.tri(splmgm)]
aspl_mgm <- mean(splmgm)

#and with tnet from opshal
spl_o = distance_w(FitW3$pairwise$wadj, directed=NULL, subsample=1)
spl_o <- spl_o[upper.tri(spl_o)]
aspl_o <- mean(spl_o)
```
ASPL = 14.0747

## Bootstrap

#### Edge accuracy

```{r}
#edge weight accuracy: non parametric bootstrap with 8 cores
#edgeacc =  bootnet(W3, nBoots = 1000, nCores = 8, 'mgm')

#load the object instead:
edgeacc = readRDS(here("Input", "edgeacc.rds"))

#plot 1
pdf('../Output/robustness/edge_accuracy.pdf', height = 70, width = 50)
plot(edgeacc, labels = longnames, order = "sample")
dev.off()

#Plot 2
pdf('../Output/robustness/edge_accuracy_CI.pdf', height = 70, width = 50)
plot(edgeacc, plot = "interval", split0 = TRUE, order="sample", labels=longnames)
dev.off()

#summary
saummary_edgeacc = summary(edgeacc, statistics = c("edge", "strength"), 
                            perNode = FALSE, rank = FALSE) 
```

#### Centrality stability

```{r}
# case dropping bootstrap
#centstab = bootnet(W3, nBoots = 1000, 'mgm', type = "case", nCores = 8)

#load the object instead:
centstab = readRDS(here("Input", "centstab.rds"))

#plot 1
pdf('../Output/robustness/Centrality_stability.pdf', height = 70, width = 50)
plot(centstab, "Strength", perNode = TRUE, labels = longnames,
     subsetRange = c(100,50))
dev.off()

#Plot 2
pdf('../Output/robustness/Centrality_stability_CI.pdf', height = 70, width = 50)
plot(centstab, "Strength", CIstyle =  "quantiles")
dev.off()

#CS-coefficient (result should be above 0.25, better if above 0.5)
corstab = corStability(centstab)
```

#### Testing Edge and centrality differences

```{r}
# Test: difference of weight ties 2-3 vs 4-5
differenceTest(edgeacc, 2--3, 3--4, "strength")

# Plot test results for every edge weight in the network
pdf('../Output/robustness/test_edges.pdf', height = 70, width = 50)
plot(edgeacc, "edge", plot = "difference", onlyNonZero = TRUE, order = "sample", 
     labels = T)
dev.off()
```

```{r}
# Test: difference of strength of node 5 [conspiracy] vs 20 [hesitancy] (if the bootstrapped CI include 0, they do not differ)
test_conspiracy_vs_hesitancy = differenceTest(edgeacc, 5, 20, "strength")

# Plot test results for every edge weight in the network
pdf('../Output/robustness/test_strenghts.pdf', height = 70, width = 50)
plot(edgeacc, "strength", order = "mean", labels = T)
dev.off()
```


## small world

```{r}
#small world network
W3_small_core = smallworldness(FitW3$pairwise$wadj, B = 1000)
W3_small_core

```
comment: 
- smallworldness > 1 -> small world network
- rnd values > 1 -> small world network
- averagelength_target (Unweighted)

## Backbone

```{r}
#model selection
backbone.suggest(FitW3$pairwise$wadj)

# application of the disparity filter
backbone_matrix <- disparity(
  inputGraphMGM,
  alpha = 0.05,
  signed = FALSE,
  mtc = "none",
  class = "original",
  narrative = TRUE)

#plot
set.seed(100)
GraphMGM<-qgraph(backbone_matrix, 
  layout = "spring", theme = "Borkulo", 
  labels = shortnames,nodeNames = longnames,
  details = FALSE, vsize=6.0, shape = shapes,
  groups=Totalgroup_comm, color= Totalgroup_cols,
  legend = TRUE, legend.cex = 0.35, borders = FALSE, 
  filetype="jpg", filename=here("Output", "backbone.jpg"))

```


## Regressions
```{r}
#Fitting logistic regressions
model_vac_bad <- glm( hesitancy ~ vac_bad + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_vac_ob <- glm( hesitancy ~ vac_ob + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_worry <- glm( hesitancy ~ worry + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_risk <- glm( hesitancy ~ risk + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_conspiracy <- glm( hesitancy ~ conspiracy + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_nat <- glm( hesitancy ~ nat + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_h_locus <- glm( hesitancy ~ h_locus + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_he_eco <- glm( hesitancy ~ he_eco + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_L <- glm( hesitancy ~ PTV_L + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_5SM <- glm( hesitancy ~ PTV_5SM + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_PTV_BOI <- glm( hesitancy ~ PTV_BOI + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_tr_sci <- glm( hesitancy ~ tr_sci + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_pray <- glm( hesitancy ~ pray + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_media <- glm( hesitancy ~ media + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_low_comp <- glm( hesitancy ~ low_comp + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_distrust_gov <- glm( hesitancy ~ distrust_gov + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)

model_distrust_inst <- glm( hesitancy ~ distrust_inst + sex + age + educ + reg + eco_insec, 
                data = W3, family = binomial)
```

```{r}
#Gathering coefficients
coeff = extract_numeric(model_vac_bad$coefficients[2])
coeff[2] = extract_numeric(model_vac_ob$coefficients[2])
coeff[3] = extract_numeric(model_worry$coefficients[2])
coeff[4] = extract_numeric(model_risk$coefficients[2])
coeff[5] = extract_numeric(model_conspiracy$coefficients[2])
coeff[6] = extract_numeric(model_nat$coefficients[2])
coeff[7] = extract_numeric(model_h_locus$coefficients[2])
coeff[8] = extract_numeric(model_he_eco$coefficients[2])
coeff[9] = extract_numeric(model_PTV_L$coefficients[2])
coeff[10] = extract_numeric(model_PTV_5SM$coefficients[2])
coeff[11] = extract_numeric(model_PTV_BOI$coefficients[2])
coeff[12] = extract_numeric(model_tr_sci$coefficients[2])
coeff[13] = extract_numeric(model_pray$coefficients[2])
coeff[14] = extract_numeric(model_media$coefficients[2])
coeff[15] = extract_numeric(model_low_comp$coefficients[2])
coeff[16] = extract_numeric(model_distrust_gov$coefficients[2])
coeff[17] = extract_numeric(model_distrust_inst$coefficients[2])

  #Transform in odds ratio
  coeff_exp = unlist(lapply(coeff, exp))

#Significance
summary(model_vac_bad)$coeff[-1,4] < 0.05
summary(model_vac_ob)$coeff[-1,4] < 0.05
summary(model_worry)$coeff[-1,4] < 0.05 #not significant
summary(model_risk)$coeff[-1,4] < 0.05
summary(model_conspiracy)$coeff[-1,4] < 0.05
summary(model_nat)$coeff[-1,4] < 0.05
summary(model_h_locus)$coeff[-1,4] < 0.05
summary(model_he_eco)$coeff[-1,4] < 0.05
summary(model_PTV_L)$coeff[-1,4] < 0.05
summary(model_PTV_5SM)$coeff[-1,4] < 0.05 #not significant
summary(model_PTV_BOI)$coeff[-1,4] < 0.05
summary(model_tr_sci)$coeff[-1,4] < 0.05
summary(model_pray)$coeff[-1,4] < 0.05 #not significant
summary(model_media)$coeff[-1,4] < 0.05 #not significant
summary(model_low_comp)$coeff[-1,4] < 0.05
summary(model_distrust_gov)$coeff[-1,4] < 0.05
summary(model_distrust_inst)$coeff[-1,4] < 0.05

  #vector for significance
  significance = rep(c(1),17)
  significance[3] = 0
  significance[10] = 0
  significance[13] = 0
  significance[14] = 0
 
#Gatering strength scores
strength = centrality_table$data$value
strength = strength[-c(15:20)]

#Gatering degree
degree_cent_graph = degree_cent[-c(15:20)]

#Gathering names
names = as.vector(names(W3))
names = names[-c(15:20)]

#Merging into a df
scatterplot = data.frame(names, coeff_exp, strength, degree_cent_graph, significance)

#as factors
scatterplot$coeff_exp = as.factor(scatterplot$coeff_exp)
scatterplot$strength = as.factor(scatterplot$strength)
scatterplot$degree_cent_graph = as.factor(scatterplot$degree_cent_graph)
scatterplot$significance = as.factor(scatterplot$significance)
```

## Scatterplot
```{r}
#Conversion
ggplot(scatterplot, aes(x=strength, y=degree_cent_graph)) + geom_point()
```


# Output

## Export heavy objects

```{r}
#communities
saveRDS(CommunityStabTotal, here("Input", "CommunityStabTotal.rds"))
#bootnet
saveRDS(edgeacc, here("Input","edgeacc.rds"))
saveRDS(centstab, here("Input", "centstab.rds"))
```

## Edge weight to excel

```{r}
##only upper triangle without edge weigths 0 for readability
EdgeWeight_Total_half<-upper.triangle(inputGraphMGM)
EdgeWeight_Total_half[EdgeWeight_Total_half == 0] <- NA
EdgeWeightsExcel_half<- list("mgm" = EdgeWeight_Total_half)
write.xlsx(EdgeWeightsExcel_half, "../Output/EdgeWeightsExcel_half.xlsx",
           colWidths = "auto", rowNames = TRUE)
```

